Programs Performance Analysis Toolkit

### 2013-10-09 keynote/Keynote.tex
Progress into evaluation part

	Rectangle[] rects2 = {
		Rectangle((5,-35), (145,-25), Label("Database interaction module"), black, lightblue),
		Rectangle((5,-50), (145,-40), Label("Program building module"), black, lightblue),
		Rectangle((5,-65), (145,-55), Label("Experimentation module"), black, lightblue),
		Rectangle((5,-80), (145,-70), Label("Information retrieval module"), black, lightblue),
		Rectangle((5,-95), (145,-85), Label("Information processing module"), black, lightblue)
	};
	draw(Block((0,-100), (150,-10), Label("Client"), black, lightgreen, rects2));

@@

>>>>

	Rectangle[] rects2 = {
		Rectangle((5,-35), (145,-25), Label("Database interaction module"), black, lightblue),
		Rectangle((5,-50), (145,-40), Label("Program building module"), black, lightblue),
		Rectangle((5,-65), (145,-55), Label("Experimentation module"), black, lightblue),
		Rectangle((5,-80), (145,-70), Label("Information retrieval module"), black, lightblue),
		Rectangle((5,-95), (145,-85), Label("Information analysis module"), black, lightblue)
	};
	draw(Block((0,-100), (150,-10), Label("Client"), black, lightgreen, rects2));

@@

\begin{frame}
\frametitle{Data analysis module}

\begin{itemize}
	\item Receives data from database and saves it to CSV files for input to \textit{Orange} statistical analysis system
	\item Graphs results using \textit{Python} library \textit{matplotlib}
	\item Two groups of program performance models
	\begin{itemize}
		\item Simplest (1 feature)
		\item More complex (3-5 features)
	\end{itemize}
	\item Four regression models in both groups
	\begin{itemize}
		\item Linear
		\item k Nearest Neighbors
		\item Multivariate Adaptive Regression Splines
		\item Random Forest
	\end{itemize}
\end{itemize}

\begin{frame}
\frametitle{Data analysis module (cont.)}
	\begin{columns}[T]
	\begin{column}{0.5\textwidth}
		\begin{itemize}
			\item Scheme of 40 data analysis components in \textit{Orange} system
			\begin{itemize}
				\item Reading in
				\item Preprocessing
				\item Filtering
				\item Feature extraction
				\item Feature ranking
				\item Predictor fitting
				\item Prediction results evaluation
				\item Saving predictions to \textit{CSV} file
			\end{itemize}
		\end{itemize}
	\end{column}
	\begin{column}{0.5\textwidth}
		\includegraphics[width=\textwidth]{series30}
	\end{column}
	\end{columns}

\section{Evaluation of implementation}
	\begin{columns}
		\begin{column}{0.5\textwidth}
			\begin{itemize}
				\item Platform
				\begin{itemize}
					\item \textit{Intel} CPUs
					\begin{itemize}
						\item \textit{Core 2 Quad Q8200} 2.33 GHz, 2 MB cache
						\item \textit{Core i5 M460} 2.53 GHz, 3 MB cache
						\item \textit{Xeon E5430} 2.66 GHz, 6 MB cache
					\end{itemize}
					\item \textit{Ubuntu 12.04}, \textit{gcc} and \textit{llvm} compilers
				\end{itemize}

				\item \textit{Polybench/C 3.2} benchmark set, 28 programs in total
				\begin{itemize}
					\item Linear algebra, solution of systems of linear algebraic equations and ordinary differential equations
				\end{itemize}
			\end{itemize}
		\end{column}
		\begin{column}{0.5\textwidth}
			\begin{itemize}
				\item Input data is generated by deterministic algorithms	
				\item Performance of chosen programs from benchmark set is modeled using \textit{Adaptor} framework
				\begin{itemize}
					\item \textit{symm}. Multiplication of symmetric matrices
					\begin{itemize}
						\item Square matrices of $2^i$ dimensionality, $i = f^{''}_{rand}(1,10)$
					\end{itemize}

					\item \textit{ludcmp}. LU-decomposition.
					\begin{itemize}
						\item Square matrices of $f^{''}_{rand}(2,1024)$ dimensionality
					\end{itemize}
				\end{itemize}

				\item 1000 experiments per CPU
			\end{itemize}
		\end{column}
	\end{columns}

\begin{frame}
\frametitle{Feature ranking. \textit{symm} program}

	\begin{columns}
		\begin{column}{0.5\textwidth}
			\begin{itemize}
				\item \textit{Earth Importance} selected only relevant features
			\end{itemize}
		\end{column}
		\begin{column}{0.5\textwidth}
			\includegraphics[scale=0.375]{feature-ranking}
		\end{column}	
	\end{columns}

\begin{frame}
\frametitle{Feature ranking. \textit{symm} program (cont.)}

	\begin{columns}
		\begin{column}{0.5\textwidth}
			\begin{itemize}
				\item Root Relative Square Error of k Nearest Neighbors --- approx. 5\%
			\end{itemize}
		\end{column}
		\begin{column}{0.5\textwidth}
			\includegraphics[scale=0.5]{evaluation-error}
		\end{column}	
	\end{columns}

\begin{frame}
\frametitle{k Nearest Neighbors model of performance of \textit{symm} program on \textit{Q8200} CPU}
\begin{center}
\includegraphics[scale=0.2]{symm-knn-q8200}
\end{center}
\end{frame}
